Numerical simulation and entropy dissipative cure of the carbuncle instability for the shallow water circular hydraulic jump

### 2021-03-07 numerics_paper/version2/numerical_chj.tex
add minor change

To compute the boundary integrals, we approximate $q$ on each cell edge $\f_{ij}$ by the average of the two

@@

where $\bfn_{ij}$ and $|\f_{ij}|$ are
the unit outward-facing normal and edge length of edge $\f_{ij}$, respectively.

>>>>

To compute the boundary integrals, we approximate $q$ on each cell edge $\f_{ij}\in\partial S_i$ by the average of the two

@@

where $|\f_{ij}|$ is the length of $\f_{ij}$ and 
$\bfn_{ij}$ is the unit vector normal to $\f_{ij}$ pointing outward from cell $i$.
%where $n_{ij}$ and $|\f_{ij}|$ are the unit outward-facing normal and edge length of edge $\f_{ij}$, respectively.
